---
title: "Untitled"
author: "JINCHEN GONG"
date: "2023-10-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(psych)
library(dplyr)
library(glmnet)
library(ggplot2)
library(car)  # VIF
library(tidyverse)
library(faraway) # Mallow's cp
library(leaps)  # Mallow's cp
source("multiplot.R")
set.seed(100)
```


| English Term                             | Chinese Translation       |
|------------------------------------------|---------------------------|
| D number of individual                   | 个体的D数量                |
| Body fat                                 | Siri's (1956) 方程式的体脂百分比 |
| Density                                  | 通过水下称重确定的密度      |
| Age (years)                              | 年龄 (岁)                 |
| Weight (lbs)                             | 体重 (磅)                 |
| Height (inches)                          | 身高 (英寸)               |
| Adioposity (bmi)                         | 体脂率 (BMI)              |
| Neck circumference (cm)                  | 颈围 (厘米)               |
| Chest circumference (cm)                 | 胸围 (厘米)               |
| Abdomen circumference (cm)               | 腹围 (厘米)               |
| Hip circumference (cm)                   | 臀围 (厘米)               |
| Thigh circumference (cm)                 | 大腿围 (厘米)             |
| Knee circumference (cm)                  | 膝围 (厘米)               |
| Ankle circumference (cm)                 | 踝围 (厘米)               |
| Biceps (extended) circumference (cm)     | 臂围（伸直）(厘米)        |
| Forearm circumference (cm)               | 前臂围 (厘米)             |
| Wrist circumference (cm)                 | 手腕围 (厘米)             |




```{r}
BodyFat <- read.csv("BodyFat.csv", header = T)
BodyFat$WEIGHT=BodyFat$WEIGHT*0.45359237
BodyFat$HEIGHT=BodyFat$HEIGHT*2.54
head(BodyFat)
describe(BodyFat)
BodyFat %>% arrange(desc(BODYFAT))%>% head()
BodyFat %>% arrange((BODYFAT))%>% head()
```


```
tbodyfat<-495/BodyFat$DENSITY-450
BodyFat$tbodyfat=tbodyfat
bodyfatdif<-log(tbodyfat)-log(BodyFat$BODYFAT)
bodyfatdifrate<-(abs(bodyfatdif))/log(BodyFat$BODYFAT)
outliers<-which(bodyfatdifrate>0.3)
BodyFat[outliers, c(1,2,3,4,5,6,17,18)]
```


- If most of the data points are located on a diagonal line, then we can assume that this diagonal line may represent a linear relationship between BODYFAT and 1/DENSITY. Our goal is to find data points that are not on this line, which are outliers.

- Here is a handy way to find the numbers of these points that are not on the line:

- Linear model fitting: We first fit a linear model using the lm() function.

- Calculate residuals: For linear relationships, the residuals (the difference between the observed value and the fitted line) are 0 or close to 0. Those points with large residuals may be outliers.

- Determining outliers: We can set a threshold, such as 2x standard deviation, to determine which data points have residuals that exceed this threshold and consider them outliers.


```{r}
model0 <- lm(1/DENSITY ~ BODYFAT, data = BodyFat)
residuals <- resid(model0)
outliers <- which(abs(residuals) > 1.5 * sd(residuals))
BodyFat[outliers,]
```

## png("plot.png")

### dev.off() 
```{r}
# Notice that there are some points not on the line
png("DENSITY-BODYFAT regression plot.png")
ggplot(BodyFat, aes(x = BODYFAT, y = 1/DENSITY)) + 
  geom_point() + 
  geom_point(data = BodyFat[outliers, ], color = "red", size = 3)+
  geom_line(data = BodyFat, aes(x = 495/DENSITY - 450), color = "blue")
dev.off() 

```

```{r}
png("Height Hist.png")
pHeight <- ggplot(data = BodyFat)+
  geom_histogram(aes(HEIGHT),binwidth = 3,color="white")
pHeight
outliers_h<-which(BodyFat$HEIGHT<100)
BodyFat[outliers_h,]
dev.off() 

```

```{r}
png("Weight Hist.png")
pWeight <- ggplot(data = BodyFat)+
           geom_histogram(aes(WEIGHT),binwidth = 10,color="white")
pWeight
outliers_w<-which(BodyFat$WEIGHT>140)
BodyFat[outliers_w,]
dev.off() 
```

```{r}
newdata <- BodyFat[-c(42,outliers),]#,-c(1,3)]
rownames(newdata)<-NULL
write.csv(newdata,file="newdata.csv")
```

```{r}
summary(newdata)
```

